Including EW and mixed QCD-EW corrections into PDF fits

### 2020-04-07 paper/sec-pineappl.tex
comments in multi-copling expansion

\subsection{Cross sections in a multi-coupling expansion}
\label{sec:multi-coupling-expansion}

>>>>

\subsection{Cross sections in a multi-coupling expansion}
\label{sec:multi-coupling-expansion}
{\bf MZ comments:}
\begin{itemize}
    \item I would prefer to keep the notation similar to the aMCfast paper, or at least to start with that, and then generalise it
    \item drop eq 2.2, start already by 2.1 with a symmetric treatment of $\alpha$ and $\alpha_s$ (plus, the symbol $\sigma$ is overloaded there)
    \item $Q$ is the Ellis-Sexton scale, a (unphysical) scale introduced to have all logs in the form $\log(\mu_R/F / Q)$, and hence to separate
        the dependence of $\mu_R$ and $\mu_F$
    \item the business of the different kinematics (born, resolved, counterterms, etc) is not mentioned at all
    \item eq 2.1 assumes $\sigma_{ab}$ integrated over phase-space?
\end{itemize}
{\bf end MZ comments:}
